Practical guides for implementing 'Five Pillar' principles

### 2023-06-11 guides/practical_guides.Rmd
Update practical_guides.Rmd

@@

@@

@@

@@

>>>>

* [Video Tutorial: Git and GitHub for Beginners - Crash Course](https://www.youtube.com/watch?v=RGOj5yH7evk)

* [Video Tutorial: Git basics - 4 short video tutorials](https://git-scm.com/videos)

* [Quick Guide: Git for humans](https://speakerdeck.com/alicebartlett/git-for-humans)

@@

* [Ebook:Happy Git and GitHub for the useR](https://happygitwithr.com/index.html)

* [Ebook: Reproducible workflow and version control with Git and Github](https://jules32.github.io/2016-07-12-Oxford/git/)

@@

* [Ebook: Version Control with Git](https://swcarpentry.github.io/git-novice/)

* [Tutorial: Using Git source control in VS Code](https://code.visualstudio.com/docs/sourcecontrol/overview)

@@

* [Video Tutorial: Reproducible Data Analysis with Snakemake](https://www.youtube.com/watch?v=hPrXcUUp70Y)

* [Tutorial: Understanding Snakemake](https://vincebuffalo.com/blog/2020/03/04/understanding-snakemake.html)

@@

* [Quick Guide: Using snakemake to do simple wildcard operations on many, many, many files](http://ivory.idyll.org/blog/2021-snakemake-simple-operations.html)
